Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-07 docs/00-manuscripts/ieee/ieee-manuscript.tex
A.B. review: error measure adjustments
A.B. review: rephrase

\subsection{Predictive Performance}
The best aggregated performance of this study (SVM + Carscore filter, RMSE 27.98 p.p.) has to be seen in the light of model overfitting (see \autoref{subsec:perf-plot-char}).
Leaving out the performance on Laukiz2 when aggregating results, the mean RMSE would be 19.
However, leaving out a single plot would also change the prediction results for the other plots because the observations from Laukiz2 would not be available for model training.
With the clear presence of model overfitting in this study it can be postulated that more training data representing all health stages of a plot is needed.
A model can only make robust predictions if it has learned relationships across the whole range of the response.
Hence, care should be taken when making statements about the overall performance of the fitted models of this study due to their high variance when predicting.
However, when inspecting the fold level performances, one can say that the model does a decent job predicting defoliation ranging from 50\% to 100\% but fails for 0\% - 50\%.
This applies to all learners of this study.

>>>>

\subsection{Predictive Performance}
The best aggregated performance of this study (SVM + Carscore filter, RMSE 27.98 p.p.) has to be seen in the light of model overfitting (see \autoref{subsec:perf-plot-char}).
Leaving out the performance on Laukiz2 when aggregating results, the mean RMSE would be 19 p.p..
However, leaving out a single plot would also change the prediction results for the other plots because the observations from Laukiz2 would not be available for model training.
With the clear presence of model overfitting in this study it can be postulated that more training data representing all health stages of a plot is needed.
A model can only make robust predictions if it has learned relationships across the whole range of the response.
Hence, care should be taken when predicting to the landscape scale using models fitted on this dataset due to their lack of generalizability caused by a suboptimal distributed training data.
However, when inspecting the fold level performances, one can say that the model does a decent job predicting defoliation ranging from 50\% to 100\% but fails for 0\% - 50\%.
This applies to all learners of this study.
